Examining relationships in R

### 2024-07-02 text/01/impact-of-population-size.Rmd
Updated 21/ihme-model

---
title: The minimal impact of population size on power and precision
author: Steve Simon
date: 2001-01-19
categories:
- Blog post
tags:
- Confidence intervals
- Sample size justification
output: html_document
page_update: complete
---

>>>>

---
title: The minimal impact of population size on power and precision
author: Steve Simon
date: 2001-01-19
categories:
- Blog post
tags:
- Confidence intervals
- Rmarkdown code
- Sample size justification
output: html_document
page_update: complete
---

### 2024-07-02 text/04/early-stopping-animal.Rmd
Updated 21/ihme-model

---
title: Early stopping in an animal study
author: Steve Simon
date: 2004-07-01
categories:
- Blog post
tags:
- Early stopping
output: html_document
---

@@

```{r, echo=TRUE}
n <- 5000
p4 <- rep(NA,n)
p8 <- rep(NA,n)
p12 <- rep(NA,n)
for (i in 1:n) {
  x1 <- rnorm(12)
  x2 <- rnorm(12)
  p4[i] <- t.test(x1[1:4],x2[1:4])$p.value
  p8[i] <- t.test(x1[1:8],x2[1:8])$p.value
  p12[i] <- t.test(x1[1:12],x2[1:12])$p.value
}
sum(p4<0.05)/n
sum(p8<0.05)/n
sum(p12<0.05)/n
sum(pmin(p4,p8,p12)<0.05)/n
```

>>>>

---
title: Early stopping in an animal study
author: Steve Simon
date: 2004-07-01
categories:
- Blog post
tags:
- Early stopping
- Rmarkdown code
output: html_document
page_update: partial
---

@@

```{r early-stopping-animal-01, echo=TRUE}
n <- 5000
p4 <- rep(NA,n)
p8 <- rep(NA,n)
p12 <- rep(NA,n)
for (i in 1:n) {
  x1 <- rnorm(12)
  x2 <- rnorm(12)
  p4[i] <- t.test(x1[1:4],x2[1:4])$p.value
  p8[i] <- t.test(x1[1:8],x2[1:8])$p.value
  p12[i] <- t.test(x1[1:12],x2[1:12])$p.value
}
sum(p4<0.05)/n
sum(p8<0.05)/n
sum(p12<0.05)/n
sum(pmin(p4,p8,p12)<0.05)/n
```

### 2024-07-02 text/05/merging-in-r.Rmd
Updated 21/ihme-model

---
title: Merging in R
author: Steve Simon
date: 2005-07-26
categories:
- Blog post
tags:
- Being updated
- R software
output: html_document
---
Merging is tricky in any program, and you have to be sure that you know
what you are doing. I have found that keeping an index variable will
allow me to backtrack and find information in the original files if
needed. Here's a simple example of how this would work.

```{r}
# randomly select 20 letters without replacement.
x0 <- sample(letters,20)
x1 <- sample(letters,20)
x0
x1
```

@@

```{r}
intersect(x0,x1)
```

@@

```{r}
setdiff(x0,x1)
setdiff(x1,x0)
```

@@

```{r}
x2 <- merge(list(x=x0,id0=1:20),list(x=x1,id1=1:20))
x2
```

@@

```{r}
x3 <- merge(list(x=x0,id0=1:20),list(x=x1,id1=1:20),all=T)
x3
```

@@

```{r}
x0 %in% x1
```

@@

```{r}
x1 %in% x0
```

@@

```{r}
x0[x0 %in% x1]
```

or the setdiff function,
```{r}
x0[!x0 %in% x1]
```

A less intuitive version of the %in% operator is the match function. Additional information on merging can be found at

- [www.ats.ucla.edu/stat/r/notes/managing.htm](http://www.ats.ucla.edu/stat/r/notes/managing.htm)

@@

>>>>

---
title: Merging in R
author: Steve Simon
date: 2005-07-26
categories:
- Blog post
tags:
- Being updated
- R software
- Rmarkdown code
output: html_document
page_update: partial
---
Merging is tricky in any program, and you have to be sure that you know
what you are doing. I have found that keeping an index variable will
allow me to backtrack and find information in the original files if
needed. Here's a simple example of how this would work.

```{r merging-in-r-01}
# randomly select 20 letters without replacement.
x0 <- sample(letters,20)
x1 <- sample(letters,20)
x0
x1
```

@@

```{r merging-in-r-02}
intersect(x0,x1)
```

@@

```{r merging-in-r-03}
setdiff(x0,x1)
setdiff(x1,x0)
```

@@

```{r merging-in-r-04}
x2 <- merge(list(x=x0,id0=1:20),list(x=x1,id1=1:20))
x2
```

@@

```{r merging-in-r-05}
x3 <- merge(list(x=x0,id0=1:20),list(x=x1,id1=1:20),all=T)
x3
```

@@

```{r merging-in-r-06}
x0 %in% x1
```

@@

```{r merging-in-r-07}
x1 %in% x0
```

@@

```{r merging-in-r-08}
x0[x0 %in% x1]
```

or the setdiff function,
```{r merging-in-r-09}
x0[!x0 %in% x1]
```

A less intuitive version of the %in% operator is the match function. Additional information on merging can be found at the [UCLA Statistics website][ucl].

@@

[ucl]: www.ats.ucla.edu/stat/r/notes/managing.htm

### 2024-07-02 text/08/declining-count-model.Rmd
Updated 21/ihme-model

---
title: Modeling a declining count variable
author: Steve Simon
date: 2008-06-14
categories:
- Blog post
tags:
- Poisson regression
output: html_document
---
I've been working on an interesting project that requires Poisson
regression. A company sends out a mailing and gets a certain number of
telephone calls back on each of the days following. The number of phone
calls is typically (but not always) highest on the first day afterwards
and declines rapidly on successive days. I wanted to develop a simple
Poisson regression model for this data.

@@

```{r}
ct <- c(9,4,2,3,0,0,1)
tm <- 0:6
pmod <- glm(ct~tm,family=poisson)
```

@@

```{r}
round(predict(pmod),4)
```

@@

```{r}
round(exp(predict(pmod)),4)
```

@@

You can sum the infinite series from time=0 to time=infinity if you
like. Notice that the terms in the above expression can be represented
by a classic [geometric
series](http://en.wikipedia.org/wiki/Geometric_series)

@@

You can find an [earlier version](http://www.pmean.com/08/DecliningCount.html) of this page on my [original website](http://www.pmean.com/original_site.html).

>>>>

---
title: Modeling a declining count variable
author: Steve Simon
date: 2008-06-14
categories:
- Blog post
tags:
- Poisson regression
- Rmarkdown code
output: html_document
page_update: partial
---
I've been working on an interesting project that requires Poisson
regression. A company sends out a mailing and gets a certain number of
telephone calls back on each of the days following. The number of phone
calls is typically (but not always) highest on the first day afterwards
and declines rapidly on successive days. I wanted to develop a simple
Poisson regression model for this data.

@@

```{r declining-count-model-01}
ct <- c(9,4,2,3,0,0,1)
tm <- 0:6
pmod <- glm(ct~tm,family=poisson)
```

@@

```{r declining-count-model-02}
round(predict(pmod),4)
```

@@

```{r declining-count-model-03}
round(exp(predict(pmod)),4)
```

@@

You can sum the infinite series from time=0 to time=infinity if you
like. Notice that the terms in the above expression can be represented
by a classic [geometric
series][wik1].

@@

You can find an [earlier version][sim1] of this page on my [original website](http://www.pmean.com/original_site.html).

[sim1]: http://www.pmean.com/08/DecliningCount.html
[sim2]: http://www.pmean.com/original_site.html

[wik1]: http://en.wikipedia.org/wiki/Geometric_series

### 2024-07-02 text/11/standard-deviation-ci.Rmd
Updated 21/ihme-model

---
title: Calculating a confidence interval for a standard deviation
author: Steve Simon
date: 2011-07-10
categories:
- Blog post
tags:
- Confidence intervals
output: html_document
---

@@

```{r}
qchisq(0.025, 79)
```

@@

```{r}
qchisq(0.975, 79)
```

>>>>

---
title: Calculating a confidence interval for a standard deviation
author: Steve Simon
date: 2011-07-10
categories:
- Blog post
tags:
- Confidence intervals
- Rmarkdown code
output: html_document
page_update: complete
---

@@

```{r standard-deviation-ci-01}
qchisq(0.025, 79)
```

@@

```{r standard-deviation-ci-02}
qchisq(0.975, 79)
```

### 2024-07-02 text/14/axis.Rmd
Updated 21/ihme-model

---
title: "Some simple examples of manipulating the axes in a graph"
author: "Steve Simon"
source: "http://www.pmean.com/axis.html"
date: "2014-01-01"
category: Blog post
tags: Sample size
output: html_document
---

@@

```{r basic-cubic}
x <- seq(-2,2,length=1000)
y <- x^3-2*x
plot(x,y)
```

@@

```{r move-tick-marks}
xticks <- c(-sqrt(2),-sqrt(2/3),0,sqrt(2/3),sqrt(2))
plot(x,y,axes=FALSE)
axis(side=2)
axis(side=1,at=xticks)
```

@@

```{r nicer-labels}
plot(x,y,axes=FALSE)
axis(side=2)
axis(side=1,at=xticks,labels=round(xticks,3))
```

@@

```{r math-expressions}
plot(x,y,axes=FALSE)
xlabs <- c(expression(-sqrt(2)),expression(-sqrt(2/3)),expression(0),expression(sqrt(2/3)),expression(+sqrt(2)))
axis(side=2)
axis(side=1,at=xticks,labels=xlabs)
```

@@

```{r crossed-axes}
xticks <- c(-sqrt(2),-sqrt(2/3),sqrt(2/3),sqrt(2))
xlabs <- c(expression(-sqrt(2)),expression(-sqrt(2/3)),expression(sqrt(2/3)),expression(+sqrt(2)))
plot(x,y,axes=FALSE)
axis(side=2,pos=0,at=c(-4,-2,2,4))
axis(side=1,at=xticks,labels=xlabs,pos=0)
```

@@

```{r new-labels}
plot(x,y,xlab="Abcissa",ylab="Ordinate")
```

@@

```{r tick-label-orientation}
# las=0 is the default
par(mfrow=c(2,2))
par(las=0)
plot(x,y)
title("las=0: Both parallel")
par(las=1)
plot(x,y)
title("las=1: Both horizontal")
par(las=2)
plot(x,y)
title("las=2: Both perpendicular")
par(las=3)
plot(x,y)
title("las=3: Both vertical")
```

@@

```{r square-plot}
par(pty="s")
plot(x,y)
```

@@

```{r equal-axis-limits}
par(pty="s")
plot(x,y,xlim=c(-4,4),ylim=c(-4,4))
abline(a=0,b=1)
```

>>>>

---
title: "Some simple examples of manipulating the axes in a graph"
author: "Steve Simon"
source: "http://www.pmean.com/axis.html"
date: "2014-01-01"
category: Blog post
tags:
- Data visualization
- Rmarkdown graphs
output: html_document
page_update: partial
---

@@

```{r axis-01}
x <- seq(-2,2,length=1000)
y <- x^3-2*x
plot(x,y)
```

@@

```{r axis-02}
xticks <- c(-sqrt(2),-sqrt(2/3),0,sqrt(2/3),sqrt(2))
plot(x,y,axes=FALSE)
axis(side=2)
axis(side=1,at=xticks)
```

@@

```{r axis-03}
plot(x,y,axes=FALSE)
axis(side=2)
axis(side=1,at=xticks,labels=round(xticks,3))
```

@@

```{r axis-04}
plot(x,y,axes=FALSE)
xlabs <- c(expression(-sqrt(2)),expression(-sqrt(2/3)),expression(0),expression(sqrt(2/3)),expression(+sqrt(2)))
axis(side=2)
axis(side=1,at=xticks,labels=xlabs)
```

@@

```{r axis-05}
xticks <- c(-sqrt(2),-sqrt(2/3),sqrt(2/3),sqrt(2))
xlabs <- c(expression(-sqrt(2)),expression(-sqrt(2/3)),expression(sqrt(2/3)),expression(+sqrt(2)))
plot(x,y,axes=FALSE)
axis(side=2,pos=0,at=c(-4,-2,2,4))
axis(side=1,at=xticks,labels=xlabs,pos=0)
```

@@

```{r axis-06}
plot(x,y,xlab="Abcissa",ylab="Ordinate")
```

@@

```{r axis-07}
# las=0 is the default
par(mfrow=c(2,2))
par(las=0)
plot(x,y)
title("las=0: Both parallel")
par(las=1)
plot(x,y)
title("las=1: Both horizontal")
par(las=2)
plot(x,y)
title("las=2: Both perpendicular")
par(las=3)
plot(x,y)
title("las=3: Both vertical")
```

@@

```{r axis-08}
par(pty="s")
plot(x,y)
```

@@

```{r axis-09}
par(pty="s")
plot(x,y,xlim=c(-4,4),ylim=c(-4,4))
abline(a=0,b=1)
```

### 2024-07-02 text/14/qqplot.Rmd
Updated 21/ihme-model

---
title: "The qqplot"
author: "Steve Simon"
source: "http://www.pmean.com/qqplot.html"
date: "2014-01-01"
category: 
- Blog post
tags:
- Checking assumptions  
- Linear regression
- R software
output: html_document
page_update: partial
---

This program was written by Steve Simon, http://www.pmean.com, and is available at http://www.pmean.com/14/qqplot.html.

See a list of my other R programs at http://www.pmean.com/category/Rsoftware.html

@@

```{r read-and-display-data}
fn <- "http://www.pmean.com/00files/housing.txt"
al <- read.table(file=fn,header=TRUE)
head(al)
tail(al)
```

```{r descriptive-statistics}
al$age <- as.numeric(al$AgeYears)
summary(al$Price)
summary(al$SquareFeet)
summary(al$age)
summary(al$NumberFeatures)
summary(al$Northeast)
summary(al$CustomBuild)
summary(al$CornerLot)
```

@@

```{r normal-probability-plot}
qqnorm(al$Price)
```

@@

```{r regression model}
al.model <- lm(Price~SquareFeet+CustomBuild,data=al)
summary(al.model)
qqnorm(resid(al.model))
```

>>>>

---
title: "The qqplot"
author: "Steve Simon"
source: "http://www.pmean.com/qqplot.html"
date: "2014-01-01"
category: 
- Blog post
tags:
- Checking assumptions  
- Linear regression
- R software
- Rmarkdown graphs
output: html_document
page_update: partial
---

@@

```{r qqplot-01}
fn <- "http://www.pmean.com/00files/housing.txt"
al <- read.table(file=fn,header=TRUE)
head(al)
tail(al)
```

```{r qqplot-02}
al$age <- as.numeric(al$AgeYears)
summary(al$Price)
summary(al$SquareFeet)
summary(al$age)
summary(al$NumberFeatures)
summary(al$Northeast)
summary(al$CustomBuild)
summary(al$CornerLot)
```

@@

```{r qqplot-03}
qqnorm(al$Price)
```

@@

```{r qqplot-04}
al.model <- lm(Price~SquareFeet+CustomBuild,data=al)
summary(al.model)
qqnorm(resid(al.model))
```

### 2024-07-02 text/15/difference-of-two-exponentials.Rmd
Updated 21/ihme-model

---
title: "Nonlinear regression for the difference of two exponentials"
author: "Steve Simon"
source: "http://blog.pmean.com/difference-of-two-exponentials/"
date: "2015-10-05"
category: 
- Blog post
tags:
- incomplete page
- nonlinear regression
- R software
output: html_document
---

@@

```{r}
head(Theoph)
```

```{r}
tail(Theoph)
```

>>>>

---
title: "Nonlinear regression for the difference of two exponentials"
author: "Steve Simon"
source: "http://blog.pmean.com/difference-of-two-exponentials/"
date: "2015-10-05"
category: 
- Blog post
tags:
- incomplete page
- nonlinear regression
- R software
- Rmarkdown graphs
output: html_document
page_update: complete
---

@@

```{r difference-in-two-exponentials-01}
head(Theoph)
```

```{r difference-in-two-exponentials-02}
tail(Theoph)
```

### 2024-07-02 text/15/missing-values-in-r.Rmd
Updated 21/ihme-model

```{r}
sl <- read.table(file="http://www.statsci.org/data/general/sleep.txt",header=TRUE)
dim(sl)
```

```{r}
names(sl)
```

@@

```{r}
head(sl)
```

```{r}
tail(sl)
```

@@

```{r}
summary(sl)
```

@@

```{r}
table(table(sl$Species))
```

```{r}
length(unique(sl$Species))
```

@@

```{r}
table(sl$Gestation)
```

@@

```{r}
addmargins(table(sl$Gestation))
```

@@

```{r}
table(sl$Gestation,useNA="always")
```

@@

```{r}
table(sl$Gestation,useNA="ifany")
```

```{r}
table(sl$Danger,useNA="ifany")
```

```{r}
table(sl$Danger,useNA="always")
```

@@

```{r}
mean(sl$Gestation,na.rm=FALSE)
```

```{r}
mean(sl$Gestation,na.rm=TRUE)
```

```{r}
mod1 <- lm(TotalSleep~Gestation,data=sl,na.action=na.omit)
summary(mod1)
```

@@

```{r}
which(sl$Gestation==NA)
```

@@

```{r}
which(is.na(sl$Gestation))
```

@@

```{r}
which(is.finite(sl$Gestation))
```

@@

```{r}
sl$Gestation==NA
```

@@

```{r}
sl$Gestation==645
```

@@

```{r}
tst.na <- NA
tst.na==tst.na
```

@@

```{r}
tst.tvl <- c(TRUE,FALSE,NA)
not.table <- !tst.tvl
names(not.table) <- tst.tvl
not.table
```

@@

```{r}
and.table <- outer(tst.tvl,tst.tvl,"&")
dimnames(and.table) <- list(tst.tvl,tst.tvl)
and.table
```

@@

```{r}
or.table <- outer(tst.tvl,tst.tvl,"|")
dimnames(or.table) <- list(tst.tvl,tst.tvl)
or.table
```

@@

```{r}
sl$Gestation<50
```

@@

```{r}
1/0
```

```{r}
-1/0
```

```{r}
sqrt(-1)
```

@@

```{r}
Inf>3
```

```{r}
NaN>3
```

```{r}
Inf==Inf
```

```{r}
NaN==NaN
```

@@

```{r}
Inf+1
```

```{r}
1/Inf
```

```{r}
0*Inf
```

```{r}
Inf-Inf
```

@@

```{r}
sqrt(as.complex(-1))
```

@@

```{r}
tst.cases <- c(3,NA,NaN,Inf,-Inf)
is.na.table <- is.na(tst.cases)
names(is.na.table) <- tst.cases
is.na.table
```

```{r}
is.finite.table <- is.finite(tst.cases)
names(is.finite.table) <- tst.cases
is.finite.table
```

>>>>

```{r missing-values-in-r-01}
sl <- read.table(file="http://www.statsci.org/data/general/sleep.txt",header=TRUE)
dim(sl)
```

```{r missing-values-in-r-02}
names(sl)
```

@@

```{r missing-values-in-r-03}
head(sl)
```

```{r missing-values-in-r-04}
tail(sl)
```

@@

```{r missing-values-in-r-05}
summary(sl)
```

@@

```{r missing-values-in-r-06}
table(table(sl$Species))
```

```{r missing-values-in-r-07}
length(unique(sl$Species))
```

@@

```{r missing-values-in-r-08}
table(sl$Gestation)
```

@@

```{r missing-values-in-r-09}
addmargins(table(sl$Gestation))
```

@@

```{r missing-values-in-r-10}
table(sl$Gestation,useNA="always")
```

@@

```{r missing-values-in-r-11}
table(sl$Gestation,useNA="ifany")
```

```{r missing-values-in-r-12}
table(sl$Danger,useNA="ifany")
```

```{r missing-values-in-r-13}
table(sl$Danger,useNA="always")
```

@@

```{r missing-values-in-r-14}
mean(sl$Gestation,na.rm=FALSE)
```

```{r missing-values-in-r-15}
mean(sl$Gestation,na.rm=TRUE)
```

```{r missing-values-in-r-16}
mod1 <- lm(TotalSleep~Gestation,data=sl,na.action=na.omit)
summary(mod1)
```

@@

```{r missing-values-in-r-17}
which(sl$Gestation==NA)
```

@@

```{r missing-values-in-r-18}
which(is.na(sl$Gestation))
```

@@

```{r missing-values-in-r-19}
which(is.finite(sl$Gestation))
```

@@

```{r missing-values-in-r-20}
sl$Gestation==NA
```

@@

```{r missing-values-in-r-21}
sl$Gestation==645
```

@@

```{r missing-values-in-r-22}
tst.na <- NA
tst.na==tst.na
```

@@

```{r missing-values-in-r-23}
tst.tvl <- c(TRUE,FALSE,NA)
not.table <- !tst.tvl
names(not.table) <- tst.tvl
not.table
```

@@

```{r missing-values-in-r-24}
and.table <- outer(tst.tvl,tst.tvl,"&")
dimnames(and.table) <- list(tst.tvl,tst.tvl)
and.table
```

@@

```{r missing-values-in-r-25}
or.table <- outer(tst.tvl,tst.tvl,"|")
dimnames(or.table) <- list(tst.tvl,tst.tvl)
or.table
```

@@

```{r missing-values-in-r-26}
sl$Gestation<50
```

@@

```{r missing-values-in-r-27}
1/0
```

```{r missing-values-in-r-28}
-1/0
```

```{r missing-values-in-r-29}
sqrt(-1)
```

@@

```{r missing-values-in-r-30}
Inf>3
```

```{r missing-values-in-r-31}
NaN>3
```

```{r missing-values-in-r-32}
Inf==Inf
```

```{r missing-values-in-r-33}
NaN==NaN
```

@@

```{r missing-values-in-r-34}
Inf+1
```

```{r missing-values-in-r-35}
1/Inf
```

```{r missing-values-in-r-36}
0*Inf
```

```{r missing-values-in-r-37}
Inf-Inf
```

@@

```{r missing-values-in-r-38}
sqrt(as.complex(-1))
```

@@

```{r missing-values-in-r-39}
tst.cases <- c(3,NA,NaN,Inf,-Inf)
is.na.table <- is.na(tst.cases)
names(is.na.table) <- tst.cases
is.na.table
```

```{r missing-values-in-r-40}
is.finite.table <- is.finite(tst.cases)
names(is.finite.table) <- tst.cases
is.finite.table
```

### 2024-07-02 text/15/relationships-in-r.Rmd
Updated 21/ihme-model

---
title: "Examining relationships in R"
author: "Steve Simon"
source: "http://blog.pmean.com/relationships-in-r/"
date: "2015-04-03"
categories:
- Blog post
tags:
- R software
output: html_document
---

@@

```{r}
suppressMessages(suppressWarnings(library(tidyverse)))
fn <- "https://raw.githubusercontent.com/pmean/introduction-to-SAS/master/data/housing.txt"
home <- read_tsv(fn, na=".")
home
```

@@

```{r}
plot(home$sqft,home$price)
lines(lowess(home$price~home$sqft))
```

```{r}
sb <- is.finite(home$age)
plot(home$age[sb],home$price[sb])
lines(lowess(home$price[sb]~home$age[sb]))
```

@@

```{r}
cor(home[,c("price","sqft","age")],use="pairwise.complete.obs")
```

@@

```{r}
round(cor(home[,c("price","sqft","age")],use="pairwise.complete.obs"),1)
```

@@

```{r}
boxplot(home$price~home$features)
```

```{r}
boxplot(home$price~home$northeast)
```

```{r}
boxplot(home$price~home$custom_build)
```

```{r}
boxplot(home$price~home$corner_lot)
```

@@

```{r}
plot(home$price,home$northeast)
lines(lowess(home$northeast~home$price))
```

```{r}
plot(home$price,home$custom_build)
lines(lowess(home$custom_build~home$price))
```

```{r}
plot(home$price,home$corner_lot)
lines(lowess(home$corner_lot~home$price))
```

@@

```{r}
round(cor(home[,c("northeast","custom_build","corner_lot")],home$price),1)
```

>>>>

---
title: "Examining relationships in R"
author: "Steve Simon"
source: "http://blog.pmean.com/relationships-in-r/"
date: "2015-04-03"
categories:
- Blog post
tags:
- R software
- Rmarkdown graphs
output: html_document
page_update: complete
---

@@

```{r relationships-in-r-01}
suppressMessages(suppressWarnings(library(tidyverse)))
fn <- "https://raw.githubusercontent.com/pmean/introduction-to-SAS/master/data/housing.txt"
home <- read_tsv(fn, na=".")
home
```

@@

```{r relationships-in-r-02}
plot(home$sqft,home$price)
lines(lowess(home$price~home$sqft))
```

```{r relationships-in-r-03}
sb <- is.finite(home$age)
plot(home$age[sb],home$price[sb])
lines(lowess(home$price[sb]~home$age[sb]))
```

@@

```{r relationships-in-r-04}
cor(home[,c("price","sqft","age")],use="pairwise.complete.obs")
```

@@

```{r relationships-in-r-05}
round(cor(home[,c("price","sqft","age")],use="pairwise.complete.obs"),1)
```

@@

```{r relationships-in-r-06}
boxplot(home$price~home$features)
```

```{r relationships-in-r-07}
boxplot(home$price~home$northeast)
```

```{r relationships-in-r-08}
boxplot(home$price~home$custom_build)
```

```{r relationships-in-r-09}
boxplot(home$price~home$corner_lot)
```

@@

```{r relationships-in-r-10}
plot(home$price,home$northeast)
lines(lowess(home$northeast~home$price))
```

```{r relationships-in-r-11}
plot(home$price,home$custom_build)
lines(lowess(home$custom_build~home$price))
```

```{r relationships-in-r-12}
plot(home$price,home$corner_lot)
lines(lowess(home$corner_lot~home$price))
```

@@

```{r relationships-in-r-13}
round(cor(home[,c("northeast","custom_build","corner_lot")],home$price),1)
```
